---
title: "What Makes a Book Popular?"
format: html
execute:
  echo: false
  message: false
  warning: false
---

```{r, message=FALSE, warning=FALSE}
#| label: setup

library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
library(dplyr)

book_data <- read.csv("Books_Data_Clean.csv")

book_data <- book_data |>
  mutate(genre = recode(genre, "genre fiction" = "fiction")) |>
    rename(book_name = Book.Name, book_average_rating = Book_average_rating,
         publisher_revenue = publisher.revenue,  sales_rank = sales.rank,
         units_sold = units.sold, publishing_year = Publishing.Year,
         author_rating = Author_Rating, book_ratings_count = Book_ratings_count,
         gross_sales = gross.sales, sale_price = sale.price, publisher = Publisher)


```


```{r, message=FALSE, warning=FALSE}
#| cache: true

fit_model <- brm(formula = gross_sales ~ genre,
             data = book_data,
             family = gaussian(),
             silent = 2,
             refresh = 0,
             seed = 9)


ndata <- tibble(genre = c("genre fiction", "nonfiction"))

```


```{r, message=FALSE, warning=FALSE}
fit_model |>
  add_epred_draws(newdata = ndata) |>
  ungroup() |>
  select(genre, .epred) |>
  ggplot(aes(x = .epred, fill = genre)) + 
    geom_density(alpha = 0.5) + 
    labs(
      title = "Genre & Book Sales",
      subtitle = "Fiction books sell more",
      x = "Sales",
      y = "Density",
      fill = "Genre") + 
      scale_fill_manual(
        values = c("genre fiction" = "blue", "nonfiction" = "red"),
        labels = c("Fiction", "Nonfiction")
      )
```



What factors contribute to a book's popularity? My data is from Kaggle, a data science resource, consisting of books from around 500 BC until 2016 and their publishing details. I seek to understand what book characteristics relate to book popularity. By modeling the genre (fiction or nonfiction) as a linear function, I found that fiction books tend to be more more popular. They are estimated to sell, on average, around 600 more units than nonfiction books.



