---
title: "Model"
format: html
execute:
  echo: false
  message: false
  warning: false
---

```{r}
library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```

I used a Gaussian Causal Model to calculate how genre, author rating, and published language relate to book sales. The model is based off this formula:

$$
y_i = \beta_{0} + \beta_{1} (chosen\ factor)_i + \epsilon_i
$$
Details about the model used—
```{r}
#| cache: TRUE
#| echo: false
#| message: false
book_data <- read.csv("Books_Data_Clean.csv")

book_data <- book_data |>
  rename(book_name = Book.Name, book_average_rating = Book_average_rating,
         publisher_revenue = publisher.revenue,  sales_rank = sales.rank,
         units_sold = units.sold, publishing_year = Publishing.Year,
         author_rating = Author_Rating, book_ratings_count = Book_ratings_count,
         gross_sales = gross.sales, sale_price = sale.price, publisher = Publisher, author = Author)

first_model <- book_data |>
  drop_na() |>
  select(gross_sales)

fit_model <- brm(formula = gross_sales ~ genre,
             data = book_data,
             family = gaussian(),
             silent = 2,
             refresh = 0,
             seed = 9)

fit_model
```


The first graph—
```{r}
#| echo: false
tbl_regression(fit_model, intercept = TRUE)
```

The second graph—
```{r}
#| cache: TRUE
fit_model_2 <- brm(formula = gross_sales ~ author_rating,
             data = book_data,
             family = gaussian(),
             silent = 2,
             refresh = 0,
             seed = 9)

tbl_regression(fit_model_2, intercept = TRUE)
```



The third graph—

```{r}
#| cache: TRUE
fit_model_3 <- brm(formula = gross_sales ~ language_code,
             data = book_data,
             family = gaussian(),
             silent = 2,
             refresh = 0,
             seed = 9)

tbl_regression(fit_model_3, intercept = TRUE)
```

(The three factors I picked were language_codeeng, language_codespa, and language_codefre, which correspond to English, Spanish, and French respectively.)
